Multi-domain, multilingual translation with latent multi-task group dropout

### 2021-11-15 2022/acl/acl_latex.tex
revised the conclusion

\textbf{Adapter modules} Adapters have proven to be very efficient for NLP multi-task modeling \citep{houlsby19parameter,Bapna19simple,Pham20Study,pfeiffer20adapterhub}. The method consists of plugging several adapters to the intermediate layers of a pretrained Transformer and finetuning these adapters on the downstream tasks. Adapters can also be trained unsupervised in multilingual translation \citep{Philip20monolingual}. However, the hard-coded separation between the domains of different tasks may lead to a catastrophic forgetting effect \citep{pfeiffer21adapterfusion}, which is a common problem in multi-task modeling using neural networks \cite{Michael89catastrophic}. In multi-domain translation, \citet{Pham21revisiting} recently demonstrated the brittleness of domain adapters against fuzzy domain separations, out-of-domain distributions, and erroneous domain tags. Several subsequent studies have aimed to mitigate this weakness through a mixture of expert mechanisms, for example,\cite{pfeiffer21adapterfusion}.

Recently, \citet{biao21share} proposed jointly learning how to route between shared representation and language-specific representation via a conditional language-specific routing and the parameters of the underlying Transformer. This method is very related to the FusionAdapters of \cite{pfeiffer21adapterfusion}. Both approaches assume the final representation is a combination or a choice between shared representation and task-specific representations. The proximity between tasks is not taken into account in the routing mechanism. Our method proposed a different point of view on the problem of multi-task routing in the underlying network.

@@

Despite several advantages, our method has several weaknesses including the heuristically predefined number of retained groups, $k$ , and the need of domain label in the inference. In future work, we would like to provide an extensive variational framework to model both the number of retained groups, $k$ and the dropping selections. Secondly, to get rid of the requirement of domain information in the inference, we could condition the dropping selection directly on the input $x$ instead of the domain $d$. These two open questions are both very interesting and promising.
\bibliography{bibliography}
\bibliographystyle{acl_natbib}
\appendix
\section{Appendix A}
\label{appendix:a}
This section explains how we calculate $\hat{m}_l^d(\tau)$ by solving the optimization problem \eqref{eq:soft-top-k} and then how to compute the gradient $\frac{\partial \hat{m}_l^d(\tau)}{\partial \Phi_l^d}$.

>>>>

\textbf{Adapter modules} Adapters have proven to be very efficient for multi-task NLP \citep{houlsby19parameter,Bapna19simple,Pham20Study,pfeiffer20adapterhub}. In a nutshell, this technique consists in plugging several so-called adapter modules to the intermediate layers of a pretrained Transformer and finetuning these adapters on the downstream tasks. Adapters can also be trained without supervision for multilingual translation \citep{Philip20monolingual}. However, the hard-coded separation between the domains of different tasks may lead to a catastrophic forgetting effect \citep{pfeiffer21adapterfusion}, which is a common problem in multi-task modeling using neural networks \citep{Michael89catastrophic}. In multi-domain translation, \citet{Pham21revisiting} recently demonstrated the brittleness of domain adapters against fuzzy domain separations, out-of-domain distributions, and erroneous domain tags. Several subsequent studies have aimed to mitigate this weakness through a mixture of expert mechanism, for example,\cite{pfeiffer21adapterfusion}.

Recently, \citet{biao21share} proposed jointly learning how to route between shared representation and language-specific representation via a conditional language-specific routing and the parameters of the underlying Transformer. This method is closely related to the FusionAdapters of \citet{pfeiffer21adapterfusion}. Both approaches assume that the final representation\fyTodo{??} is a combination or a choice between shared representation and task-specific representations. The proximity between tasks is not taken into account in the routing mechanism. Our method proposed a different approach to the problem of multi-task routing in the underlying network.

@@

There are several ways in which our methodology could be improved and generalized. In future work, we would first like to provide an complete variational framework to model both the number of groups, $k$ and the selection of the dropout masks. Second, we also intend to get rid of the requirement of knowing the domain information during inference: this would mean replacing the dependency on $d$ in the variational distribution by a dependency in the input $x$. These two questions seem both very interesting and promising; they would allow to us to dispense with heuristic choices in the architecture, and replace them with an increase dependency on the training data.

\bibliography{bibliography}
\bibliographystyle{acl_natbib}
\appendix
\section{Appendix A}
\label{appendix:a}
This section explains how we calculate $\hat{m}_l^d(\tau)$ by solving the optimization problem \eqref{eq:soft-top-k} and then how to compute the gradient $\frac{\partial \hat{m}_l^d(\tau)}{\partial \Phi_l^d}$.
